Predicting Diabetes Based on Various Factors Using logistic Regression

### 2023-11-22 manuscript/manuscript.tex
Abstract explanation
Simple formating changes

\begin{abstract}

\end{abstract}

@@

    Previously, the prediction of diabetes has been studied using machine learning models. Specifically in Sisodia's paper, it focused on the "Prediction of Diabetes using Classification Algorithms", they worked through the topic by producing results using support vector machine, Naive Bayes classifier, and decision tree classifier (\cite{Sisodia2018Prediction}). In this paper, I will be continuing the investigation with a different data set using logistic regression and various other statistical tests..

>>>>

\begin{abstract}
This section will be completed once the paper is closer to completion. 
\end{abstract}

@@

    Previously, the prediction of diabetes has been studied using machine learning models. Specifically in Sisodia's paper, it focused
    on the "Prediction of Diabetes using Classification Algorithms", they worked through the topic by producing results using support 
    vector machine, Naive Bayes classifier, and decision tree classifier (\cite{Sisodia2018Prediction}). In this paper, I will be 
    continuing the investigation with a different data set using logistic regression and various other statistical tests.
